Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-02 src/article.tex
Revise conclusions

Scaffolder is software aimed at bioinformaticians and biologists familiar with
the command line building genome sequence scaffold. The file format maintains
the scaffold in a concise and readable way allowing third parties to see how
the genome sequence was assembled. This file format allows a broad overview of
of which sequences were included and how they are ordered possible not possible
from a megabase-sized strings of nucleotide characters. Scaffolder also
furthers the cause for reproducibility in genome projects by allowing the
scaffold super-sequence to be reliably reproduced from the scaffold file. The
YAML syntax for writing the scaffold file is also standardised and to
manipulate programmatically. This thereby means the scaffolding process follows
the Unix tenet of: ``If your data structures are good enough, the algorithm to
manipulate them should be trivial.''.

>>>>

Scaffolder is software aimed at bioinformaticians and biologists familiar with
the command line who wish to build a genome sequence scaffold. The file format
maintains the scaffold in a concise and readable way allowing third parties to
see how the genome sequence was assembled. This file format allows a broad
overview of of which sequences were included and how they are ordered,
something not possible from a megabase-length strings of nucleotide characters.
Scaffolder furthers the case for reproducibility in genome projects by allowing
the scaffold super-sequence to be reliably reproduced from the same scaffold
file. The YAML syntax for writing the scaffold file is also standardised and
simple to manipulate programmatically. This thereby means the scaffolding
process follows the Unix tenet of: ``If your data structures are good enough,
the algorithm to manipulate them should be trivial.''.
